The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-10 src/ms.tex
Discuss removal of ERFA and .vo

The relationship between \astropy and community is reciprocal, with the growing and evolving needs of the community and the maturation of the broader scientific \python ecosystem driving the development of the \astropypkg core package since \citealt{astropy:2018}.
% feels like ↑ could be expanded to 2 sentences

@@

@@

\begin{itemize}
%  \item Time Series sub-package (V3.1: New Box Least Squares Periodogram)
%  \item Uncertainties and Distributions
  \item ERFA module is now it’s own thing; Obliquely tie in that units
    remains in astropy
%  \item ? Pytest plugin ecosystem -> done elsewhere
%  \item A new SpectralCoord class for representing and transforming spectral quantities
%    Velocity in Coordinates
%  \item WCS API : A shared Python interface for World Coordinate Systems
%        Include APE 14 reference
\end{itemize}

@@

>>>>

The relationship between \astropy and community is reciprocal, with the growing and evolving needs of the community and the maturation of the broader scientific \python ecosystem driving the development of the \astropypkg core package since \citetalias{astropy:2018}.
% feels like ↑ could be expanded to 2 sentences

@@

Before discussing those, we should mention that sometimes one realizes
features do not actually belong in the core package, either because
they are of more general use outside of \astropypkg, or because they
are too specialized.  An example of the former is the copy of the IAU
Standards Of Fundamental Astronomy (SOFA) software
Collection\footnote{\url{http://www.iausofa.org}} \citep{sofa} that
astropy carried, as well as the python wrappers for it.  Since this is
more basic infrastructure, with a release cycle set by SOFA, it made
more sense to create separate packages that \astropypkg\ can depend
on: \package{ERFA} \citep{erfa} and \package{PyERFA} \citep{pyerfa}.
An example of something that was too specialized was a Virtual
Observatory sub-package (now removed).  Of its content, the Simple
Application Message Protocol made sense to keep
(\astropysubpkg{samp}), but other parts belonged more properly in {\tt
  Astroquery} (see Sect.~\ref{sec:astroquery}).

@@

% \begin{itemize}
%  \item Time Series sub-package (V3.1: New Box Least Squares Periodogram)
%  \item Uncertainties and Distributions
%   \item ERFA module is now it’s own thing; Obliquely tie in that units
%    remains in astropy -> above
%  \item ? Pytest plugin ecosystem -> done elsewhere
%  \item A new SpectralCoord class for representing and transforming spectral quantities
%    Velocity in Coordinates
%  \item WCS API : A shared Python interface for World Coordinate Systems
%        Include APE 14 reference
% \end{itemize}

@@

\label{sec:astroquery}
% MHvK: feel free to move above label to where it makes most sense.
